Verifying Demonstrations

### 2018-02-26 paper/SystemModel.tex

\subsection{Physical System Model}
In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
Section~\ref{protocol} and uploading their testimony to a blockchain
after the protest. They thus need connectivity at least to each other
during the protest and Internet connectivity after.

>>>>

\subsection{Physical System Model}
In practical terms, participants witness each other's particpation
using their smartphones running the protocol described in
\cref{protocol} and uploading their testimony to a blockchain
after the protest. They thus need connectivity at least to each other
during the protest and Internet connectivity after.
